Output Summary

### 2023-08-18 03-post-process/output-plots.Rmd
Rename param summaries Rmd section
& Improve it some
Rename post-vs-prior Rmd section
& Improve some

```{r noise-term-diags, child = "output-plots-children/11-resid-diags.Rmd", eval = params$include_resid_diags}
```

@@

```{r param-summaries, child = "output-plots-children/12-param-summaries.Rmd", eval = params$include_param_summaries}
```

```{r post-v-prior, child = "output-plots-children/13-post-vs-prior.Rmd", eval = params$include_post_v_prior}
```

>>>>

```{r noise-term-diags, child = "output-plots-children/11-resid-diags.Rmd", eval = params$include_residual_diags}
```

@@

```{r param-summaries, child = "output-plots-children/13-param-summaries.Rmd", eval = params$include_param_summaries}
```

```{r post-v-prior, child = "output-plots-children/14-post-vs-prior.Rmd", eval = params$include_post_v_prior}
```
